---
title: "Problems in Homework1"
author: "Zicheng Wang"
date: "2024-09-16"
output: github_document
---

##Problem 1
Loading the penguins dataset and necessary packeges for the problems
```{r setup}
data("penguins", package = "palmerpenguins")
library(tidyverse)
library(ggplot2)
```

Discription of the dataset:  
```{r}
rows <- nrow(penguins)
cols <- ncol(penguins)
species <- paste(unique(penguins$species), collapse = ", ")
islands <- paste(unique(penguins$island), collapse = ", ")
bi_length_min <- min(penguins$bill_length_mm, na.rm = TRUE)
bi_length_max <- max(penguins$bill_length_mm, na.rm = TRUE)
bi_depth_min <- min(penguins$bill_depth_mm, na.rm = TRUE)
bi_depth_max <- max(penguins$bill_depth_mm, na.rm = TRUE)
fl_length_min <- min(penguins$flipper_length_mm, na.rm = TRUE)
fl_length_max <- max(penguins$flipper_length_mm, na.rm = TRUE)
bm_min <- min(penguins$body_mass_g, na.rm = TRUE)
bm_max <- max(penguins$body_mass_g, na.rm = TRUE)
means <- mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The `penguins` dataset consists of measurements of penguins:
The dataset contains **`r rows`** rows and **`r cols`** columns. Have species, island, sex, bill length, bill depth, flipper length and body mass variables.  
These penguins came from three different species: **`r species`**.  
The penguins were studied on three islands: **`r islands`**.  
Bill length (in mm): ranges from **`r bi_length_min`** to **`r bi_length_max`** mm  
Bill depth (in mm): ranges from **`r bi_depth_min`** to **`r bi_depth_max`** mm  
Flipper length (in mm): ranges from **`r fl_length_min`** to **`r fl_length_max`** mm  
Body mass (in g): ranges from **`r bm_min`** to **`r bm_max`** g  
The mean flipper length of the penguins is **`r means`** mm.


Create scatterplot of Flipper length and bill length by different species
Using `theme_minimal()` as the theme
```{r}
p <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs. Bill Length by Species", 
       x = "Bill Length (mm)", 
       y = "Flipper Length (mm)") +
  theme_minimal()
```

Display the plot
```{r}
print(p)
```

Save the scatterplot to the project directory
```{r}
ggsave("Scatterplot_penguins.png", plot = p)
```

##Problem 2

Create a data frame:
```{r df_create}
df <- tibble(
  sample_normal = rnorm(10, mean = 0, sd = 1),
  sample_logic = sample_normal > 0,
  sample_char = sample(letters, 10),
  sample_level = factor(sample(c("Level1", "Level2", "Level3"), 10, replace = TRUE))
)
```

Display the data frame to inspect:  
```{r}
print(df)
```

Calculate means of each variable in the data frame:  
```{r}
mean(df %>% pull(sample_normal))
mean(df %>% pull(sample_logic))
mean(df %>% pull(sample_char))
mean(df %>% pull(sample_level))
```

Change those type of variables that cannot calculate mean into numeric type:  
```{r eval = FALSE}
df$sample_logic <- as.numeric(df$sample_logic)
df$sample_char <- as.numeric(df$sample_char)
df$sample_level <- as.numeric(df$sample_level)
```
First two lines returned following message: `Warning: NAs introduced by coercion`, the last line performed without warnings.
